A Survey of Fuzzing and New Technique for Dynamic Analysis

### 2014-02-16 docs/paper/fsuthesis/thesis-template/paper.tex
Small edits to paper
added Mayhem deets to paper

\title{A Survey of Fuzzing and New Technique for Dynamic Analysis}
\author{Clark Wood}
\college{College of Arts and Science}
\department{Department of Computer Science} % Delete if no department
\manuscripttype{Thesis}              % [Thesis, Dissertation, Treatise]
\degree{Masters of Science}                 
\semester{Spring}                            % [Spring, Summer, Fall]
\degreeyear{2014}
\defensedate{Spring 2014}

@@

\committeeperson{Zhi Wang}{Professor Directing Thesis}
%\committeeperson{Verda Boizaar}{University Representative}
%\committeeperson{Beauxeau D'Claune}{Committee Member}
%\committeeperson{Arlip Zarseeld}{Committee Member}

@@

@@

SAGE - architecture, then underlying ideas

@@

@@

\section{TODO Mayhem}

Talk about CMU Mayhem.

@@

>>>>

\title{A Survey of Fuzzing and New Technique for Dynamic Analysis}
\author{Clark Wood}
\college{College of Arts and Science}
\department{Department of Computer Science} % Delete if no department
\manuscripttype{Thesis}              % [Thesis, Dissertation, Treatise]
\degree{Masters of Science}                 
\semester{Spring}                            % [Spring, Summer, Fall]
\degreeyear{2014}
\defensedate{XXXXXXX}

@@

\committeeperson{Zhi Wang}{Professor Directing Thesis}
%\committeeperson{Beauxeau D'Claune}{Committee Member}
%\committeeperson{Arlip Zarseeld}{Committee Member}

@@

TODO focus on fact that this stands separate from and complementary to symb. exec? Perhaps performance analysis vs. s2e on binaries to show the potential?

@@

\subsection{Microsoft SAGE}

@@

Peach Fuzzer

@@

\section{TODO Mayhem, AEG, Exploitable Bugs}

Talk about CMU Mayhem. [H]
AEG [I]

While finding bugs of any sort enhances software by providing developers the opportunity to fix problems with their programs, finding bugs that lead to exploitable conditions are of special interest. A bug is exploitable if it allows adveraries to undermine confidentiality, integrity, or availability [CITE] via avenues such as information disclosure, denial of service, or remote execution of code. Because these bugs stand alone as a separate, particularly worrying class, efforts have been made to automate the process of proving whether an identified bug is also a vulnerability which can be exploited.

Mayhem, an exploitable bug-finding system, is an attempt to address this issue by exploring state space as efficiently as possible. The authors designed Mayhem to handle path explosion by monitoring system resources and balancing the need for concurrent exploration with the resources consumed by forking and running many processes. Mayhem accomplishes through hybrid symbolic execution, a technique which heuristically combines offline and online symbolic execution. Offline symbolic execution first runs a program concretely, instrumenting the process to gather information which will then be used by a separate symbolic execution engine. Online symbolic execution, instead, tries to explore the entire program symbolically by forking new processes at branches. [H]

Mayhem improves fuzzing time performance by weaving between these two modes. It is implemented as a client-server architecture, with the client running code concretely and passing specific blocks to the server for symbolic execution. Only the server outputs results or further test cases to explore concretely. The client uses block-level dynamic taint analysis, passing control to the symbolic execution server when tainted branches or jumps are discovered. Mayhem modifies its behavior based on system memory constraints, beginning in online mode and switching to offline mode when a threshhold for memory resources is reached. Upon switching, Mayhem also saves checkpoints to save its work in an attempt to reduce exploring the same code twice. [H]

TODO Mayhem techniques

AEG required source code, where Mayhem needs access only a binary to execute. Mayhem is, however, limited to a subset of all system calls for the operating system it executes on. This is deliberate on the part of the authors, who reason that OS-wide symbolic execution introduces too much overhead. Of significance as an area of future research, Mayhem, and most other fuzzing technology explored, cannot reason about taint propagated through threading mechanisms [H].

TODO similar to Automatic
patch-based exploit generation is possible: Techniques and
implications, but mine doesn't require a patch?

@@

\section{results}

TODO
